Aldebaran~b's temperate past uncovered in planet search data

### 2018-02-05 paper/aldebaran.tex
Remove comment on mass loss treatment
misc

%% e
\newcommand{\EccentricityRange}{0.17$\pm$0.07} %\twosidedrange{0.168}{0.069}{0.071}}

@@

By jointly fitting a Keplerian for the planet with a CARMA model for the stellar
oscillations to the combined archival and SONG data sets (Figure \ref{alldata}),
we obtain a precise estimate of both \numax and the planetary orbital
parameters. The planetary orbital parameters we obtain are similar to
\citet{Hatzes2015}, but with larger uncertainty that is likely due to our
more-flexible and correlated model for the stellar component of the RV signal:
period $P = \PeriodRange \, \mathrm{d}$, eccentricity $e =
\EccentricityRange{}$; and radial velocity semi-amplitude $K =
\PlanetRVAmpRange{} \, \mathrm{m} \, \mathrm{s}^{-1}$.

>>>>

%% e
\newcommand{\EccentricityRange}{0.17\pm0.07} %\twosidedrange{0.168}{0.069}{0.071}}

@@

By jointly fitting a Keplerian for the planet with a CARMA model for the stellar
oscillations to the combined archival and SONG data sets (Figure \ref{alldata}),
we obtain a precise estimate of both \numax and the planetary orbital
parameters. The planetary orbital parameters we obtain are similar to
\citet{Hatzes2015}, but with larger uncertainty that is likely due to our
more-flexible and correlated model for the stellar component of the RV signal:
period $P = \PeriodRange{} \, \mathrm{d}$,  eccentricity $e =
\EccentricityRange{}$; and radial velocity semi-amplitude $K =
\PlanetRVAmpRange{} \, \mathrm{m}\, \mathrm{s}^{-1}$.
